---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```{r}
# install.packages("classdata")
# install.packages("ggplot2")
library(ggplot2)
library(dplyr)

library(classdata)
ames

ames <- ames
```
*Step 1*
The variables contain strings, dates, and various pertinent numeric information. 
-Parcel ID is the unique variable to identify the building that was sold.
- Address is the address.
- Style contains the number of stories in a housewith other relevant information.
- Occupancy addresses the housing density.
- Sale Date is the date the house was sold.
- Sale Price is the main variable; it's how much the house sold for.
- Year Built is the year each building was made.
- Acres is the property's acreage.


*Step 2*
The main variable seems to be the price; most people care a lot more about the price than any other feature when purchasing a building.

*Step 3*


```{r, message = FALSE}
  ames2 <- ames %>% filter(`Sale Price` > 10, na.rm = TRUE)
  ggplot(ames2, aes(x = `Sale Price`)) + geom_histogram() + scale_x_log10()
```


*Step 4*
Naomi will analyze the relationship between house cost and total living area.
Brandon will analyze the relationship between house cost and year built.
Cole will analyze the relationship between house cost and acreage.
Cameron will analyze the relationship between housing cost and bedrooms


```{r, message = FALSE}
ames3 <- ames2 %>% filter(`LotArea(sf)` > 10, na.rm = TRUE)
  ggplot(ames3, aes(x = `Sale Price`, y = `LotArea(sf)`)) + scale_x_log10() + geom_point(shape = 8) + scale_y_log10()
```
*Step 4(Cole Flickinger)*
The range itself is homes within the cost of a few hundred dollars all the way to a few million dollars with square footages spanning from a couple hundred square feet all the way up to the tens of thousands. Notably, the houses appear to mostly cost around upwards of $100,000 while the square footage seems to often be a little less than 10,000 square foot with a few outlier houses going for around the same cost. There is not as strong of an upward trend of housing cost in comparison to square-footage as I initially expected. This does explain the extremely low cost house by itself in the graph that was shown during the histogram. Notably, making sense that this low cost house would also have an extremely small square-footage.

```{r, message = FALSE}
amesAge <- ames %>% filter(YearBuilt > 0, `Sale Price` > 0)
ggplot(amesAge, aes(x = YearBuilt)) + geom_histogram()
ggplot(amesAge, aes(x = log10(`Sale Price`), y = YearBuilt)) + geom_point()
```
\
Brandon Merrick Step 4:
The Year Built ranges from about 1880 to 2020 with more houses generally existing for later years.\
There appears to only be a small effect when comparing Age to Price where the majority cluster around the same area and newer houses having more variability to both be above and below average\
This does not seem to describe any oddities\



```{r, message = FALSE}
install.packages("ggpubr")
library(ggpubr)

amesArea <- ames %>% filter(`TotalLivingArea (sf)` > 0, `Sale Price` > 0)
ggplot(amesArea, aes(x = `TotalLivingArea (sf)`)) + geom_histogram()
ggplot(amesArea, aes(x = log10(`Sale Price`), y = `TotalLivingArea (sf)`)) + geom_point() + stat_cor()
amesArea2 <- ames %>% filter(`TotalLivingArea (sf)` > 0, `Sale Price` > 171975, `Sale Price` < 338088)
ggplot(amesArea2, aes(x = (`Sale Price`), y = `TotalLivingArea (sf)`)) + geom_point() + stat_cor()
summary(amesArea)

```
*Step 4 Naomi Mauss*
The minimum living area is 3 square feet, and the maximum living area is 6,007 square feet. The mean is 1,504 and the median is 1,455. A histogram shows the distribution of living area sizes skews right, with a longer tail on the right than on the left. The correlation coefficient is -0.061, which is very weak. Additionally, a negative correlation between the cost of a house and the building's square footage seems unlikely. In comparing sale price to total living area, there is an wide range of prices, even after applying a log function. Outliers could explain the unexpected correlation coefficient, so it makes sense to have another graph which considers more average variables The 1st quartile sale price is 171975, and the 3rd quartile is 338088. When considering only houses whose price is within the interquartile range, the correlation coefficient is 0.37. This makes more sense, as it is expected for a bigger house to cost more money, and there is not a weak correlation coefficient.

*Step 4 Cameron Kraklio*
The minimum number of bedrooms is zero, possibly a data error or apartment. The max is 10 with a median of 3. As partial bedrooms wouldn't make sense the mean isn't as helpful in this case, although it being higher than the median helps to show how the data is skewed right.Homes with more than 5 bedrooms were rare with 10 bedrooms being an outlier. Also interestingly nough more bedrooms didn't always indicate a higher price as some outlier high sale price homes had a relativly low bedroom count


```{r, message = FALSE}

range(ames$Bedrooms, na.rm = TRUE)
range(ames$`Sale Price`, na.rm = TRUE)
summary(ames$Bedrooms)
ggplot(ames, aes(x = `Bedrooms`, y = `Sale Price`)) + geom_point()
ggplot(ames, aes(x = `Bedrooms`)) + geom_histogram()
```
