---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```{r}
# install.packages(classdata)
# install.packages("ggplot2")
library(ggplot2)
library(dplyr)

library(classdata)
ames

ames <- ames
```
*Step 1*
The variables contain strings, dates, and various pertinent numeric information. 
-Parcel ID is the unique variable to identify the building that was sold.
- Address is the address.
- Style contains the number of stories in a housewith other relevant information.
- Occupancy addresses the housing density.
- Sale Date is the date the house was sold.
- Sale Price is the main variable; it's how much the house sold for.
- Year Built is the year each building was made.
- Acres is the property's acreage.


*Step 2*
The main variable seems to be the price; most people care a lot more about the price than any other feature when purchasing a building.

*Step 3*


```{r, message = FALSE}
  ames2 <- ames %>% filter(`Sale Price` > 10, na.rm = TRUE)
  ggplot(ames2, aes(x = `Sale Price`)) + geom_histogram() + scale_x_log10()
```


*Step 4*
Naomi will analyze the relationship between house cost and total living area.
Brandon will analyze the relationship between house cost and year built.
Cole will analyze the relationship between house cost and acreage.



```{r, message = FALSE}
  
```
